Verifying Demonstrations

### 2018-05-25 paper/SystemModel.tex
Fixes refs to non-existent labels
Edits definitions in system model

\NewVariable{\cid}{cid}

@@

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
    \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t = \interval{t_s}{t_e}\subseteq \RR\) is a time interval and \(l \subseteq 
    \RR^2\) is the location.
  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
\end{definition}

@@

We use other participants, that we called \emph{witnesses} to associate the 
proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the 
risk of inflation.
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

\NewVariable{\pid}{pid}
\NewVariable{\wid}{wid}

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \((\pid, \cid, t, l, \wid)\) is a tuple 
  where:
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a function of the protester's identity and \(\cid\); and
  \(\wid\) is a function of the witness' identity and 
  \(\pid\).
  We let \(W\) be the set of all proof shares.
\end{definition}
\sonja{do the same pair of people (witness-protester) get the
same wid on a different protest? The pid is unique for protester-cid
pair thus the id of a protester at a particular protest. Pid is thus
derived from the protester id (which has no term) and the protest id
(cid)? In analogy, wid is derived from pid (and thus cid) of both
participants, protesters i and j, say, where i witnesses j at cid and
simultaneously symmetrically j witnesses i?
Using wid and w is confusing since we changed the terminology to use
proof shares instead of the previous witness (as in testimony, not
person). wid sounds like it would be the id of the witness person,
pid sounds like it would be the id of the protester being witnessed,
we have defined neither and they might not be needed, but it is
confusing to read.}
\daniel{I made some minor changes, any better?}

@@

\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{multline}
    \nonumber
    p_{i, j} =
    \left\{ (\pid, \cid, t, l, \wid)\in W \mid \right. \\
    \left. \pid = i, \cid = j,
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witness 
  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
  (\ie \(t_j\) and \(l_j\)).
\end{definition}

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(\cid\) as the 
  cardinality \(|P_{\cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{\cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = \cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}
The strength function \(s\) can be used to regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another example would be to return the number of proof shares issued by trusted 
witnesses and set \(\theta = 1\) to require at least one proof share issued by a 
trusted witness.

@@

In practical terms, participants witness each other's participation
using their smartphones (or similar devices) running the protocol described in
\cref{protocol} and uploading their testimony (\ie proof shares) to a blockchain 
after the protest. During the protest the devices are computationally limited by 
their batteries and need local connectivity to each other but no connection to
any global network such as the Internet is necessary. Before and
after the protest, we assume that the devices have global connectivity, \ie 
Internet  connections, and are not computationally limited by any battery.

>>>>

% cause identifier
\NewVariable{\cid}{cid}

@@

% protest
\NewVariable{\prtst}{P}
% subprotest
\NewVariable{\sprtst}{p}

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
    \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location 
  (topological connectedness is not necessary).
  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
\end{definition}

@@

We use \emph{witnesses} to associate the proof to the location by creating a 
\emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the 
risk of inflation.
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

% proof share
\NewVariable{\psh}{s}
% proof shares
\NewVariable{\pshs}{S}
% protester identifier
\NewVariable{\pid}{pid}
% witness identifier
\NewVariable{\wid}{wid}

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
  tuple where:
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
  and
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
    \sqsubseteq p\).
  We let \(\pshs\) be the set of all proof shares.
\end{definition}
\sonja{do the same pair of people (witness-protester) get the
same wid on a different protest? The pid is unique for protester-cid
pair thus the id of a protester at a particular protest. Pid is thus
derived from the protester id (which has no term) and the protest id
(cid)? In analogy, wid is derived from pid (and thus cid) of both
participants, protesters i and j, say, where i witnesses j at cid and
simultaneously symmetrically j witnesses i?
\daniel{Not necessarily.}
Using wid and w is confusing since we changed the terminology to use
proof shares instead of the previous witness (as in testimony, not
person). wid sounds like it would be the id of the witness person,
pid sounds like it would be the id of the protester being witnessed,
we have defined neither and they might not be needed, but it is
confusing to read.}
\daniel{I made some minor changes, any better?}

@@

% proof
\NewVariable{\prf}{\pi}
% proofs
\NewVariable{\prfs}{\Pi}

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}
  A \emph{participation proof} of protester with pseudonym \(\pid\) 
  participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, 
  witnessing time interval \(t\) and location \(l\) is within those of the 
  protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

% strength
\NewFunction{\str}{\varsigma}

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(\prtst\) (as in 
  \cref{DefParticipationProof}) as the cardinality \(|\prfs_{P}^{\str,\theta}|\) 
  of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,j})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}
The strength function \(\str\) can be used to regulate trust in witnesses.
One example would be for \(\str\) to return the number of unique witnesses and 
thus let \(\theta\) to be the threshold of the number of required witnesses.
Another example would be to return the number of proof shares issued by trusted 
witnesses and set \(\theta = 1\) to require at least one proof share issued by a 
trusted witness.

@@

In practical terms, participants witness each other's participation
using their smartphones (or similar devices) running the protocol described in
\cref{Protocol} and uploading their testimony (\ie proof shares) to a blockchain 
after the protest. During the protest the devices are computationally limited by 
their batteries and need local connectivity to each other but no connection to
any global network such as the Internet is necessary. Before and
after the protest, we assume that the devices have global connectivity, \ie 
Internet  connections, and are not computationally limited by any battery.
